### 2024-01-14 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024

\begin{dedication}
\begin{center}
    \section*{Acknowledgements}
\end{center}
\justify{

@@

Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors. Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuoussupport has been pivotal at every stage of my thesis. I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I h\
ave experienced through his invaluable guidance.

>>>>

\begin{dedication}
\begin{center}
    \section*{Acknowledgement}
\end{center}
\justify{

@@

Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors. Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis. I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.
